---
title: "How Can a Wellness Technology Company Play It Smart?"
author: "Ankita Gairola"
date: "2023-07-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This case study from the Google Data Analytics professional Certificate. 


## 1. Ask

Bellabeat is a high-tech manufacturer of health-focused products for women. Since it was founded in 2013, Bellabeat has grown rapidly and quickly
positioned itself as a tech-driven wellness company for women. 

The aim of this project to analyze smart device usage data in order to gain insight into how consumers use non-Bellabeat smart
devices.

Questions:

1. What are some trends in smart device usage?
2. How could these trends apply to Bellabeat customers?
3. How could these trends help influence Bellabeat marketing strategy?

Deliverable:

1. A clear summary of the business task
2. A description of all data sources used
3. Documentation of any cleaning or manipulation of data
4. A summary of your analysis
5. Supporting visualizations and key findings
6. Your top high-level content recommendations based on your analysis.

## 2. Prepare

Data Source : Kaggle and contain 18 csv file

Sample size: 30 Fitbit users

Data Period: 12 March 2016 to 12 May 2016

## 3. Process

##### Set working Directory

getwd()

setwd("E:/Capstone projects_Google/Case Study 2")

##### Required Packages

install.packages("tidyverse")

install.packages("readxl")

install.packages("skimr")

install.packages("janitor")

install.packages("lubridate")

install.packages("scales")

install.packages("here")

install.packages("dplyr")

install.packages("ggplot2")

install.packages("RColorBrewer)

```{r}
library("tidyverse")

library("readxl")

library("skimr")

library("janitor")

library("lubridate")

library("scales")

library("here")

library("ggplot2")

library("dplyr")

library(RColorBrewer)

```


##### Data Importing

```{r}
Daily_Activity <- read.csv("E:/Capstone projects_Google/Case Study 2/Data Set/Fitabase Data 4.12.16-5.12.16/dailyActivity_merged.csv")

Daily_Calories <- read.csv("E:/Capstone projects_Google/Case Study 2/Data Set/Fitabase Data 4.12.16-5.12.16/dailyCalories_merged.csv")

Daily_Steps <- read.csv("E:/Capstone projects_Google/Case Study 2/Data Set/Fitabase Data 4.12.16-5.12.16/dailySteps_merged.csv")

Sleep_Day <- read.csv("E:/Capstone projects_Google/Case Study 2/Data Set/Fitabase Data 4.12.16-5.12.16/sleepDay_merged.csv")

Daily_Intensities <- read.csv("E:/Capstone projects_Google/Case Study 2/Data Set/Fitabase Data 4.12.16-5.12.16/dailyIntensities_merged.csv")

Weight_Log <- read.csv("E:/Capstone projects_Google/Case Study 2/Data Set/Fitabase Data 4.12.16-5.12.16/dailyIntensities_merged.csv")


```

##### Overview of data

```{r}
skim_without_charts(Daily_Activity)

skim_without_charts(Daily_Calories)

skim_without_charts(Daily_Intensities)

skim_without_charts(Daily_Steps)

skim_without_charts(Sleep_Day)

skim_without_charts(Weight_Log)
```



```{r}
colnames(Daily_Activity)

colnames(Daily_Calories)

colnames(Daily_Intensities)

colnames(Daily_Steps)

colnames(Sleep_Day)

colnames(Weight_Log)

```
##### Data Cleaning

###### Data Information checking

```{r}
str(Daily_Activity)

str(Daily_Calories)

str(Daily_Intensities)

str(Daily_Steps)

str(Sleep_Day)

str(Weight_Log)
```

###### Any Missing value

```{r}
which(is.na(Daily_Activity))

which(is.na(Daily_Calories))

which(is.na(Daily_Intensities))

which(is.na(Daily_Steps))

which(is.na(Sleep_Day))

which(is.na(Weight_Log))
```

###### Number of unique participants

```{r}
n_distinct(Daily_Activity$Id)

n_distinct(Daily_Calories$Id)

n_distinct(Daily_Intensities$Id)

n_distinct(Daily_Steps$Id)

n_distinct(Sleep_Day$Id)

n_distinct(Weight_Log$Id)
```
## 4. Analyze

##### Summary of Data

```{r}
summary(Daily_Activity)

summary(Daily_Calories)

summary(Daily_Intensities)

summary(Daily_Steps)

summary(Sleep_Day)

summary(Weight_Log)
```

##### Visualization

###### Finding relationship between steps and calories from Daily_Activity data with Graphs

```{r}
ggplot(data = Daily_Activity) +
  geom_col(mapping = aes(x = Calories, y = TotalSteps), fill = "blue")

```


```{r}
ggplot(data = Sleep_Day) + geom_smooth(mapping= aes(x=TotalMinutesAsleep, y=TotalTimeInBed),color = "blue") + geom_point(mapping= aes(x=TotalMinutesAsleep, y=TotalTimeInBed),color= "white")
```


###### Relationship between steps and sedentary minutes in Daily_Activity with Graphs

```{r}
ggplot(data = Daily_Activity, aes(x=TotalSteps, y=SedentaryMinutes, colour = "red")) + geom_point()
```

###### Finding relationship between total time in bed and total minutes asleep from Sleep_Day Data 

```{r}
ggplot(data = Sleep_Day, aes(x = TotalMinutesAsleep, y = TotalTimeInBed, color = "green")) +geom_point()

```
```{r}
ggplot(data = Sleep_Day) + geom_smooth(mapping= aes(x=TotalMinutesAsleep, y=TotalTimeInBed),color = "red") + geom_point(mapping= aes(x=TotalMinutesAsleep, y=TotalTimeInBed),color= "blue")
```



###### Finding relationship between Very Active Minutes and Very Active Distance from Weight_Log data with Graphs

```{r}

ggplot(data = Weight_Log) +
  geom_col(mapping = aes(x = VeryActiveMinutes, y = VeryActiveDistance), fill = "blue")
```

##### Merging Daily Activity and Sleep Day dataset

```{r}
DailyActivity_SleepDay <- merge(Daily_Activity, Sleep_Day, all = TRUE)

view(DailyActivity_SleepDay)

colnames(DailyActivity_SleepDay)
```
###### Number of unique participants in combined dataset

```{r}
n_distinct(DailyActivity_SleepDay$Id)
```
###### User activities in minutes through Pie Chart

```{r}
Sedentary <- sum(DailyActivity_SleepDay$SedentaryMinutes)
Active <- sum(DailyActivity_SleepDay$VeryActiveMinutes)
Fairly <- sum(DailyActivity_SleepDay$FairlyActiveMinutes)
Lightly <- sum(DailyActivity_SleepDay$LightlyActiveMinutes)

x <- c(Sedentary,Lightly,Fairly,Active)
labels <- c("Sedentary", "Lightly Active", "Fairly Active", "Very Active")

piepercent <- round(100*x/sum(x),1)

labels <- paste0(piepercent,"%")

colour = brewer.pal(length(piepercent), "Set2")

pie(x,labels = labels, main = "Active Minutes Pie Chart", col = colour, cex = 0.65)


legend("topright",c("Sedentary","Lightly Active", "Fairly Active", "Very Active"), cex = 0.9, fill = colour)

```


###### Add a new coloumn in the combined dataset converting 'char' into 'Date'.

```{r}
DailyActivity_SleepDay$ActivityDate2 <- mdy(DailyActivity_SleepDay$ActivityDate)

colnames(DailyActivity_SleepDay)
```
###### convert activity date into days of week.

```{r}
DailyActivity_SleepDay$weekday <- wday(DailyActivity_SleepDay$ActivityDate2, label = TRUE)

colnames(DailyActivity_SleepDay)

head(DailyActivity_SleepDay$weekday)
```


```{r}
ggplot(data = DailyActivity_SleepDay, aes(x = weekday)) + geom_bar(fill = brewer.pal(7, "Set2")) + labs(title = "User logged activity in a week", x = "Day of week", y = "Activity Frequency")
```

## 5. Share

1. Positive correlation between total steps and calories burnt.
2. Negative correlation between total steps and sedenatary minutes.
3. Positive correlation between total minutes in bed and total minutes asleep.
4. Daily activity high in mid of the week.


















